Opt-K

### 2013-03-14 paper/paper.tex
test hooks
Started adding validation results to the paper. This is definitely messy, but it's a start.

\usepackage{amsmath}    % need for subequations
\usepackage{amssymb}    % for symbols
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
%\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs

\begin{document}

@@

\section{Validation}
We being by using the procedure described above on the M\"{u}ller potential.

>>>>

\usepackage{amsmath}    % need for subequations
\usepackage{amssymb}    % for symbols
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
%\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
\usepackage[capitalise]{cleveref}   % use for referencing figures/equations
\begin{document}

@@

\section{Validation}

\subsection{Langevin Dynamics on the M\"uller Potential}
We being by using the procedure described above on data generated by simulating Langevin dynamics on the M\"{u}ller potential (\cref{fig:muller_pot}). This data was clustered into models of different sizes using one of two algorithms. The first, K-Centers, tends to make equal sized states as it works to minimize the maximum distance between a conformation and its generator. The second, Hybrid, will make varying size states because it works to minimize the average distance between conformations and their generators. In both cases, we built models ranging from 50 to 1,000 total states. Since this space is only two-dimensional, we used the simple, brute-force MC algorithm for calculating volumes.

Briefly, we generated uniform random vectors within a bounding box whose size was slightly larger than the data. This random sample was then accepted if it was 'close enough' to a generator in the 100 state model, where close enough meant it was within 0.2 units from any generator in that model. This was used to approximate the convex hull of the data. Then the accepted points were assigned to a state. Then the volume of a state is proportional to the number of samples assigned to that state divided by the total number of samples. We note, that these volumes are actually in units of the total acceptable volume. This affects the absolute value of the likelihood, however, since the total volume was constant in all cases, the relative likelihoods are the same.

\begin{figure}[h!]
\includegraphics[width=3in]{figs/muller_pot_traj.pdf}
\caption{The M\"{u}ller potential consists of three metastable wells. We simulated Langevin dynamics on this potential as validation of the new likelihood function.}
\label{fig:muller_pot}
\end{figure}

\begin{figure}
\includegraphics[width=2in]{figs/like_comp.pdf}
\end{figure}
